Introducing SCM to a small company

### 2012-01-11 article.tex
plan

The configuration plan can be written in two different approaches.
cite{SCMPLAN} It can either be done before the implementation of SCM in a big bang approach or we can use a more iterative method and complete the plan meanwhile the project goes on.
Since we are new to the role as a configuration manager and don't have a precise definition on the company and its details it might be too hard to go with the iterative approach.
This way we can start with the most important parts of the SCM plan in the beginning.

To write a good configuration plan can be hard, it is different for every company and will determinate the future of SCM in the future.
A good SCM plan can rise a sinking company as well sink a well working.
In an article written by Bounds and Dart they describe the SCM plan as one of the three most important keys to successfully attain a SCM solution /cite{BoundsDart}.
It is possible to write one all by yourself as a configuration manager but with our small experience in the area we will take help from someone with more skills.
We will also have good contact with the product manager to make this plan as good as possible.

Since it is so hard to write a good SCM plan we will need more help then a helping person. There are several standards to build a frame or a skeleton upon but one cannot be suitable for all companies, there cannot be one universal standard.
The three most popular are NASA, IEEE and DOD. \cite{SCMPLAN}

A SCM plan is a good checklist for the configuration manager to check whether all is kept in mind for the SCM implementation or something is missed.
When all the checkpoints are completed we have a completed SCM plan to work upon and we know we have thought of all the details.
Once the configuration plan is completed it's not finished.
Changes are often made to the project which will have impact on the plan, we therefore need to change the configuration plan as well so it is always updated.
This is one of the reasons why we need to have the configuration plan as a configuration item (CI) which we will describe later on in the paper.

A complete configuration plan will cover everything to implement SCM to a specific company and is a very large document.
Here in this report we will therefore only discuss a few aspects of it which we decide are the most important and interesting.

>>>>

The configuration plan can be written in two different approaches. \cite{SCMPLAN} It can either be done before the implementation of SCM in a big bang approach or we can use a more iterative method and complete the plan meanwhile the project goes on. 
Since we are new to the role as a configuration manager and don’t have a precise definition on the company and its details it might be too hard to go with the iterative approach. This way we can start with the most important parts of the SCM plan in the beginning

To write a good configuration plan can be hard, it is different for every company and will determinate the future of SCM in the future. A good SCM plan can rise a sinking company as well sink a well working. In an article written by Bounds and Dart they describe the SCM plan as one of the three most important keys to successfully attain a SCM solution \cite{BoundsDart}.  It is possible to write one all by yourself as a configuration manager but with our small experience in the area we will take help from someone with more skills. We will also have good contact with the product manager to make this plan as good as possible.

Since it is so hard to write a good SCM plan we will need more help then a helping person.
There are several standards to build a frame or a skeleton upon but one cannot be suitable for all companies, there cannot be one universal standard.
The three most popular are ISO, IEEE and DOD but NASA is also used. \cite{SCMPLAN}
NASA is often used for larger companies and projects and will not be suitable for our small target. The DOD, Department of Defense, standard was used by the military from the beginning but can also be used for companies. We want to have  standard which covers the whole organization and not only the current project, this is however not possible with the DOD standard and we will therefore not use this either.
ISO is a well working standard in industries where we have different management systems and procedures. The Problem Company is a software company with very little or none benefit of such standard.
The standard we will work with is the IEEE which Bounds and Dart measures have the highest rating with a study of 6 criteria (ease of use, completeness, tailorability, consistency, correctness and life cycle connection). IEEE is a very tailorable standard which is good for The Problem Company. There are also more benefits but to choose the standard is not what we want to focus on in this article.

A SCM plan is a good checklist for the configuration manager to check whether all is kept in mind for the SCM implementation or something is missed. When all the checkpoints are completed we have a completed SCM plan to work upon and we know we have thought of all the details. Once the configuration plan is completed it’s not finished. Changes are often made to the project which will have impact on the plan, we therefore need to change the configuration plan as well so it is always updated. This is one of the reasons why we need to have the configuration plan as a configuration item (CI) which we will describe later on in the paper.

A complete configuration plan will cover everything to implement SCM to a specific company and is a very large document. Here in this report we will therefore only discuss a few aspects of it which we decide are the most important and interesting. The SCM plan will discuss how to solve The Problem Companiy's problems.
